---
title: "Draft R Markdown document"
author: "Morten Dall"
output: html_document
---
##import raw data
```{r setup}
library(vroom)
library(here)
```

```{r}
user_1_info_file <- here("data-raw/mmash/user_1/user_info.csv")
user_1_info_data <- vroom(
  user_1_info_file,
  col_select = -1,
  col_types = cols(
    Gender = col_character(),
    Weight = col_double(),
    Height = col_double(),
    Age = col_double()
  ),
  .name_repair = snakecase::to_snake_case)

user_1_info_data
                          
  ```
```

##Exercise: import of saliva data

```{r}
user_1_saliva_file <- here("data-raw/mmash/user_1/saliva.csv")
user_1_saliva_data_prep <- vroom(user_1_saliva_file,
                                 col_select = -1)

spec(user_1_saliva_data_prep)

user_1_saliva_data <- vroom(
    user_1_saliva_file,
    col_select = -1,
    col_types = cols(
  SAMPLES = col_character(),
  `Cortisol NORM` = col_double(),
  `Melatonin NORM` = col_double()),
    .name_repair = snakecase::to_snake_case
)

user_1_saliva_data
```

##importing larger datasets

```{r}
user_1_rr_file <- here("data-raw/mmash/user_1/RR.csv")
user_1_rr_data <- vroom(
  user_1_rr_file,
  col_select = -1,
  col_types = cols(
    ibi_s = col_double(),
    day = col_double(),
    time = col_time(format = "")),
    .name_repair = snakecase::to_snake_case)

user_1_rr_data


```

##Exercise: Import the Actigraph data

```{r}
user_1_actigraph_file <- here("data-raw/mmash/user_1/Actigraph.csv")
user_1_actigraph_data_temp <- vroom(user_1_actigraph_file,
                                    n_max = 100,
                                    col_select = -1)
user_1_actigraph_data <- vroom(user_1_actigraph_file,
                               col_select = -1,
                               col_types = cols(
                                 Axis1 = col_double(),
                                 Axis2 = col_double(),
                                 Axis3 = col_double(),
                                 Steps = col_double(),
                                 HR = col_double(),
                                 `Inclinometer Off` = col_double(),
                                 `Inclinometer Standing` = col_double(),
                                 `Inclinometer Sitting` = col_double(),
                                 `Inclinometer Lying` = col_double(),
                                 `Vector Magnitude` = col_double(),
                                 day = col_double(),
                                 time = col_time(format = "")),
                               .name_repair = snakecase::to_snake_case)


```
```{r}
import_user_info(here("data-raw/mmash/user_1/user_info.csv"))
```

